%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{ben-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Zhesi Ben}{Ning}{ \urlstyle{same}\href{https://github.com/gdzhben}{github.com/gdzhben} | \href{https://www.benzning.com/}{benzning.com} |
\href{https://www.linkedin.com/in/ben-ning/}{linkedin.com/in/ben-ning} | +353 87 359 8608 | \href{mailto:zhesi.ning@ucdconnect.ie}{zhesi.ning@ucdconnect.ie}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.37\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University College Dublin}
\descript{MSc in Business Analytics}
\location{Graduated Dec 2019 | Dublin, Ireland}
Michael Smurfit Graduate Business School\\
\location{ Grade : 2.1 }
\sectionsep

\subsection{University College Dublin}
\descript{BS in Computer Science}
\location{Graduated Sep 2018 | Dublin, Ireland}
School of Computer Science \\
\location{ Grade : 2.1 }
\sectionsep

\section{PROJECTS}
\runsubsection{Predicting time-to-sell for classified ads}
\descript{| Data Science}
Data science project which involve build predictive models to predict time-to-sell for classified ads which accompanied with exploratory analysis of the data and model interpretation. Code written in Python and some common data science package were used, such as pandas, scikit-learn, PySurvival.
\sectionsep

\runsubsection{Backgammon Tournament Analyser}
\descript{| Simulation}
%\location{\href{https://github.com/gdzhben/FYP39380-Backgammon-Tournament-Analysis-17-18}{github.com/gdzhben/FYP39380-Backgammon-Tournament-Analysis-17-18}}
This project runs Monte Carlo simulation to estimate the accuracy of the existing backgammon winning probability models using computer roll outs. Developed a model for the duration of human player matches using the computer roll outs and measurement of real games by running the open source GNU Backgammon (GNUbg).
\sectionsep

\runsubsection{Risk Game}
\descript{| Game}
\location{\href{https://github.com/gdzhben/risk-game}{github.com/gdzhben/risk-game}}
Risk game is a Java implementation of the Risk Board Game. Java Swing was used to build its GUI for interacting with the user. This was a team project and implemented as a part of college assignment.
\sectionsep

\runsubsection{WithHer Poker}
\descript{| ChatBot\&Game}
\location{\href{https://github.com/gdzhben/withHerPoker}{github.com/gdzhben/withHerPoker}}
Twitter-based implementation of five card draw Poker written in Typescript. Contains a bot that listens to direct messages for a twitter account, MongoDB were used to store the state of the game.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.61\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SKILLS} 
\subsection{TECHNICAL SKILLS}
Python 3 \textbullet Git \textbullet Linux 
\subsection{SOFT SKILLS}
Problem solving ability \textbullet Agile \textbullet Waterfall \textbullet Customer facing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{WORK EXPERIENCE}
\runsubsection{DISTILLED SCH}
\descript{| Data Science Intern }
\location{May 2019 - Sep 2019 | Dublin, Ireland}
\vspace{\topsep}
\begin{tightemize}
\item Communicated with business stakeholders to understand business problems.

\item Gathered necessary data from multiple data sources from a read-only Amazon Redshift database(PostgreSQL) and managed data quality.

\item Conducted exploratory data analysis to reveal insights from motors Ads on Distilled SCH's platform DoneDeal.ie with Jupyter Notebook and JupyterHub on a scalable Linux distribution.

\item Built data visualisation dashboard to provide insight into motor business data using Tableau and Matplotlib.

\item Developed predictive models using machine learning techniques in Python using Scikit-learn.

\item Leveraged analytical and reporting skills to support DoneDeal define possible new premium user features.
\end{tightemize}
\sectionsep

\runsubsection{UCD}
\descript{| Module Demonstrator }
\location{June 2014 – Sep 2014 | Dublin, Ireland}
\begin{tightemize}
\item Collaborated with a team of 5 tutors teaching a number of computer science modules for non-cs major students.

\item Coordinated coursework and continuous assessment during practical sessions for a class of up to 100 students.
\end{tightemize}
\sectionsep

\runsubsection{UCD}
\descript{| Teaching Assistant }
\location{May 2013 – Aug 2013 | Dublin, Ireland}
\begin{tightemize}
\item Tutored undergraduate computer science students, covering material related to algorithmic problem solving, Java, Unix and introductory programming concepts.

\item Graded numbers of scripts and programming assignments; gave feedback to individual students.

\item Resolved students’ inquiries, communicated with students on an individual basis regarding their courseworks.
\end{tightemize}
\sectionsep

\runsubsection{Wandsoft}
\descript{| Software Developer Intern}
\location{Jan 2016 – May 2016 | Dublin, Ireland}
\begin{tightemize}
\item Developed new features with a team of 5 software engineers for a web-based CRM system and provided solutions to ease GDPR compliance(Adobe ColdFusion and HTML).

\item Updated existing CRM database(SQL) and developed new queries to accommodate new features required by GDPR.

\item Created new screens within the end-user interface for an audit database.

\item Gained exposure to a variety of technologies pertinent to database management, testing, networks and version control.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
